Improving reproducibility of scientific software using Nix/NixOS: A case study on preCICE adapters and solvers

### 2024-05-03 paper/paper.tex
feat: short title
chore: more friendly wording in intro

\title{Improving reproducibility of scientific software using Nix/NixOS: A case study on preCICE adapters and solvers}
\short{TODO}
\author{
Max Hausch\autref{1+},
Simon Hauser\autref{2+},
Benjamin Uekermann\autref{3}}

@@

Attempts were made by scientists like Koch et al.~\cite{koch2023sustainable} to solve this situation by using Docker\footnote{\url{https://www.docker.com/}}, a software which describes software environments with the help of text files.
Those text files are made up of imperative commands which are run inside of containers, one layer at a time.
The result are several different layers which are all combines into a single output image that can be instantiated to a running container.
Docker images can be copied to different hosts and should then provide the same environment on different machines.
An issue that arises here, is that usually those images are based on one of the official Docker images\footnote{\url{https://docs.docker.com/trusted-content/official-images/}} all of which bring traditional package managers like \texttt{apt}.
When a user specifies to install the \texttt{python3} package with a traditional package manager today, the package manager could yield python3.8, whereas running the same command two months from now could yield python in the version 3.9.
This could potentially lead to different results when a user wants to only add a single dependency but has to rebuild the whole image, thus rendering it useless in terms of reproducibility.

>>>>

\title{Improving reproducibility of scientific software using Nix/NixOS: A case study on preCICE adapters and solvers}
\short{preCICE on Nix: A case study}
\author{
Max Hausch\autref{1+},
Simon Hauser\autref{2+},
Benjamin Uekermann\autref{3}}

@@

Attempts were made by scientists like Koch et al.~\cite{koch2023sustainable} to solve this situation by using Docker\footnote{\url{https://www.docker.com/}}, a software which describes software environments with the help of text files.
Those text files are made up of imperative commands which are run inside of containers, one layer at a time.
The result are several different layers which are all combines into a single output image that can be instantiated to a running container.
Docker images can be copied to different hosts and should then provide the same environment on different machines.
An issue that arises here, is that usually those images are based on one of the official Docker images\footnote{\url{https://docs.docker.com/trusted-content/official-images/}} all of which bring traditional package managers like \texttt{apt}.
When a user specifies to install the \texttt{python3} package with a traditional package manager today, the package manager could yield python3.8, whereas running the same command two months from now could yield python in the version 3.9.
This could potentially lead to different results when a user wants to add a single dependency but has to rebuild the whole image, thus rendering it inpractical in terms of reproducibility.
